% ----------------------------------------------------------------------------------------
% SECTION TITLE
% ----------------------------------------------------------------------------------------

\cvsection{Work Experience}

% ----------------------------------------------------------------------------------------
% SECTION CONTENT
% ----------------------------------------------------------------------------------------

\begin{cventries}

  % ------------------------------------------------
    
  \cventry
    {the freebsd project}
    {Google Summer of Code, FreeBSD}
    {Kanpur, India}
    {Apr. 2018 - Present}
    {
      \begin{cvitems}
        \item Built a Regression Test-Suite for FreeBSD's audit subsystem using libraries from Automated Testing Framework and ported it within the existing Test-Suite. 
        \item Contributed more than 400 test-cases for 50 system calls classified in TCP/IP \& UDP sockets, File I/O, process control and device management.
        \item Used various BSD kernel functions and libbsm APIs to test the audit events by I/O multiplexing on a special clonable device, /dev/auditpipe.
        \item Collaborated with FreeBSD commiters around the world to enhance the security features of the operating system.  
      \end{cvitems}
    }
  
  \cventry
    {lucideus technologies}
    {Security Analyst Intern}
    {New Delhi, India}
    {Nov. 2017 - Jan. 2018}
    {
      \begin{cvitems}
        \item Developed and deployed a secure social networking platform in LAMP Stack. Assessed its vulnerability against OWASP top 10 attacks and improved the security. 
        \item Extensively used VAPT tools like Metasploit, Wireshark, Xerosploit, Nessus, Maltego and many more.
        \item Researched cyptographical model implementation in Network and Wireless Security, analysed WEP encryption weaknesses and exloited using aircrack-ng.
        \item Reverse engineered Windows applications to understand and mitigate common security flaws.  
      \end{cvitems}
    }

 \cventry
    {programming Club}
    {Full Stack Web Development}
    {Kanpur, India}
    {May. 2017 - July. 2017}
    {
      \begin{cvitems}
        \item Developed a scalable web application for nominations of various posts of Students' Gymkhana, IITK .
        \item Used Django along with Django-Rest-Framework and PostgreSQL for developing the portal.  
        \item	Implemented dynamic heirarchy levels, search feature and multiple model versions in the backend API. Designed a Responsive User Interface from scratch using Bootstrap and jQuery.
        \item Selected as one of the Top \textbf{6} projects from all Science and Technology Clubs to give final presentation.
      \end{cvitems}
    }
    
  \cventry
  {Antaragni - 17}
  {Senior Web Executive}
  {Kanpur, India}
  {July'2017 - Oct'2017}
  {
    \begin{cvitems}
    \item Used the full \textbf{MEAN Stack} in Typescript for a fest webapp and its admin control panel.
    \item Dynamic website with content easily changeable via the control panel. Supported Android App with an API.
    \item Technologies Used - NodeJS, AngularJS, MongoDB, ExpressJS and more
    \end{cvitems}
  }
  


  % ------------------------------------------------
\end{cventries}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../resume_twopage"
%%% End:
