% ----------------------------------------------------------------------------------------
% SECTION TITLE
% ----------------------------------------------------------------------------------------

\cvsection{Projects}

% ----------------------------------------------------------------------------------------
% SECTION CONTENT
% ----------------------------------------------------------------------------------------

\begin{cventries}

  % ------------------------------------------------
 \cventry
    {summer Project, Programming Club}
    {Full Stack Web Development}
    {Kanpur, India}
    {May. 2017 - July. 2017}
    {
      \begin{cvitems}
          \item Developed a scalable web application for nominations of various posts of Gymkhana, IITK .
  \item Used Django along with Django-Rest-Framwork and PostgreSQL for developing the portal.  
  \item	Implemented dynamic heirarchy levels, search feature, django-filter and multiple model versions in the backend API.
  \item Designed a Responsive User Interface from scratch using Bootstrap and jQuery.
      \end{cvitems}
    }

 \cventry
    {semester project, association Computing Activities}
    {Computational Complexity Theory}
    {Kanpur, India}
    {IInd Semester}
    {
      \begin{cvitems}
         \item Reading Project on Theory of Computation. Studied about non-deterministic complexity classes eg. NP, NP-Complete, NP-Hard.
  \item Researched the fundamental working of \textbf{Turing Machine} and its properties. Analyzed famous NP-Complete problems, e.g SAT, Hamiltonian Path, Travelling Salesman etc. 
  \item Understood the implication of Complexity Theory in Quantum Computing and Cryptography.
  \item Prepared the final report in \LaTeX{} which is now under examination. 
      \end{cvitems}
    }

  % ------------------------------------------------
\end{cventries}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../resume_twopage"
%%% End:
